Clustering time series based on probability distributions across temporal granularities

### 2021-11-17 main.Rmd

It is common to pre-process data prior to fitting a supervised learning model using instance selection [@olvera2010review] which removes observations that might impede the model building. For clustering, this is analogous to identifying and removing nuisance observations. Prototype selection is more severe than instance selection, because a handful of cases is selected. @cutler proposed a method called archetypal analysis which has inspired this approach but the procedure we have used follows @Fan2021-bq. First  dimension reduction such as t-SNE, MDS or PCA is used to project the data into a 2D space. Second a few  "anchor" customers far apart in 2D space are selected. Additional close neighbors to the anchors are selected. To check the selections relative to the full set of variables, we used a tour linked to a t-SNE layout using the R package `liminal` [@R-liminal]. This ensured that the final sample of clustered customers were also far apart in the high-dimensional space. (See the supplementary materials for further details.) <!--Few of these customers have similar distribution across $moy$ and some are similar in their $hod$ distribution. -->

>>>>

It is common to pre-process data prior to fitting a supervised learning model using instance selection [@olvera2010review] which removes observations that might impede the model building. For clustering, this is analogous to identifying and removing nuisance observations. Prototype selection is more severe than instance selection, because a handful of cases is selected. @Cutler1994-hm proposed a method called archetypal analysis which has inspired this approach but the procedure we have used follows @Fan2021-bq. First  dimension reduction such as t-SNE, MDS or PCA is used to project the data into a 2D space. Second a few  "anchor" customers far apart in 2D space are selected. Additional close neighbors to the anchors are selected. To check the selections relative to the full set of variables, we used a tour linked to a t-SNE layout using the R package `liminal` [@R-liminal]. This ensured that the final sample of clustered customers were also far apart in the high-dimensional space. (See the supplementary materials for further details.)<!--Few of these customers have similar distribution across $moy$ and some are similar in their $hod$ distribution. -->
